### 2015-01-19 src/methodology.Rnw
update

\subsubsection{E-Selective}
\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
three main classes of operators; Replacement (operand) mutators, Expression (operator)
mutators and Statement mutators. The operator selections used in this paper
are groupings of these operators, such as ES, ER, RS, RS, and E.

@@

@@

\subsubsection{Variable Reduction}
\noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
For variable reduction, Namin framed the question of finding the best set of
mutation operators as a statistical problem of finding the set of operators
such that we can best predict the final mutation score. That is, given that
$M$ is the final mutation score, and $m_1,m_2..m_n$ are mutation scores given
by $n$ mutation operators, Namin wanted to find the smallest set of mutations
such that we can predict $M$ from the set of $m_{1..n}$. This boils down to
finding the linear model

\[M = \alpha m_1 + \beta m_2 ... \omega m_n\]

where $\alpha,\beta .. \omega$ are constants. However we take advantage of the
limited set of operators to run a complete subset model comparison to obtain
the best model given by
\[\mu{M_s} = 0+.55 nmc + .2 rc + .1 dc + .2 rv + .1 cc + .7emv + .02 m + .02 ri \]

>>>>

\subsubsection{E-Selective}
\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
three main classes of operators; Replacement (operand) mutators, Expression (operator)
mutators and Statement mutators. The operator selections used in this paper
are groupings of these operators, such as ES, ER, RE, RS, and E.

@@

We report the results of all combinations: ES, ER, RS, E, R, and S

@@

\subsubsection{Variable Reduction}
\noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
For variable reduction, Namin framed the question of finding the best set of
mutation operators as a statistical problem of finding the set of operators
such that we can best predict the final mutation score. That is, given that
$M$ is the final mutation score, and $m_1,m_2..m_n$ are mutation scores given
by $n$ mutation operators, Namin wanted to find the smallest set of mutations
such that we can predict $M$ from the set of $m_{1..n}$. This boils down to
finding the linear model statistically.

We take advantage of the limited set of operators to run a complete subset
model comparison to obtain the best model given by

\[\mu{M_s} = 0+.55 nmc + .2 rc + .1 dc + .2 rv + .1 cc + .7emv + .02 m + .02 ri \]
